---
title: 'Joanna Jaimes: Career Outcomes IR'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Welcome

Hello! This document will serve to display the Career Outcomes data work that I will be doing throughout the summer. 

## Observations about te Career Outcomes Data Set

Earliest year is 1999. Most recent date is 2018.
Various countries represented in the data. For example, 1021 graduates have come from Thailand, 79 from Uruguay, and 272 from Mexico.

```{r}

library(haven)
careeroutcomes <- read_sas("careeroutcomes.sas7bdat")

library(haven)
careeroutcomes <- read_sas("careeroutcomes.sas7bdat", 
    NULL)
View(careeroutcomes)

# summaries
# summary(careeroutcomes$Degree)
# summary(careeroutcomes$Chairs)
# summary(careeroutcomes$JobType)
# summary(careeroutcomes)
# summary(careeroutcomes$citizenship_status_descr)


#tables

table(careeroutcomes$Calendar_Yr) 
table(careeroutcomes$citizenship_country_descr) 
table(careeroutcomes$Deg_FY)


# library(psych)
# describe(careeroutcomes)
```

## Do graduates from particular fields of study pursue post doctoral positions more often than other fields of study?

```{r}
# Jobs and Field of study 

library(dplyr)

# Base R

table(careeroutcomes$rack_division_descr)

table(careeroutcomes$rack_division_descr,
      careeroutcomes$JobType)

# dplyr


library(ggplot2)

careeroutcomes%>%
  group_by(JobType,rack_division_descr) %>% 
  tally()%>%
  ggplot(aes(x = rack_division_descr, 
             y=n,
             fill = rack_division_descr)) + geom_bar(stat="identity") + facet_wrap(~JobType)


```

## Narrowing in Using SinceGrad_Yr


```{r}

# Isoloate Years
SinceGrad1 <- careeroutcomes %>% filter(SinceGrad_Yr==1)
SinceGrad2 <- careeroutcomes %>% filter(SinceGrad_Yr==2)
SinceGrad3 <- careeroutcomes %>% filter(SinceGrad_Yr==3)
SinceGrad4 <- careeroutcomes %>% filter(SinceGrad_Yr==4)
SinceGrad5 <- careeroutcomes %>% filter(SinceGrad_Yr==5)
SinceGrad6 <- careeroutcomes %>% filter(SinceGrad_Yr==6)
SinceGrad7 <- careeroutcomes %>% filter(SinceGrad_Yr==7)
SinceGrad8 <- careeroutcomes %>% filter(SinceGrad_Yr==8)
SinceGrad9 <- careeroutcomes %>% filter(SinceGrad_Yr==9)
SinceGrad10 <- careeroutcomes %>% filter(SinceGrad_Yr==10)
SinceGrad11 <- careeroutcomes %>% filter(SinceGrad_Yr==11)
SinceGrad12 <- careeroutcomes %>% filter(SinceGrad_Yr==12)
SinceGrad13 <- careeroutcomes %>% filter(SinceGrad_Yr==13)
SinceGrad14 <- careeroutcomes %>% filter(SinceGrad_Yr==14)
SinceGrad15 <- careeroutcomes %>% filter(SinceGrad_Yr==15)
SinceGrad16 <- careeroutcomes %>% filter(SinceGrad_Yr==16)
SinceGrad17 <- careeroutcomes %>% filter(SinceGrad_Yr==17)
SinceGrad18 <- careeroutcomes %>% filter(SinceGrad_Yr==18)
SinceGrad19 <- careeroutcomes %>% filter(SinceGrad_Yr==19)
SinceGrad20 <- careeroutcomes %>% filter(SinceGrad_Yr==20)

  
  
SinceGrad1 %>%
  arrange(JobType) %>%
  tally()
  ggplot(SinceGrad1,
         aes(x = JobType,
             fill =as.factor(rack_division_descr))) + 
  geom_bar() +
    scale_fill_viridis_d() +
    ylim(-1000, 2500) +
    theme( 
          panel.grid = element_blank(), 
          plot.margin = unit(rep(-1,100), "cm",)) +
    coord_polar(start = 0) 
    
   
    

```


```{r, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
